Note about WSC

### 2015-03-25 notes.tex
results with simple trade 2 goods 600 agents

@@

As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law).

>>>>

The Gintis' innovation mechanism differ from those used in cultural evolution literature (such as mechanism used by \cite{bentley2004randomdriftandculturechange,mesoudi2009randomcopyingfrequencydependencopyingandulturechange}). In the literature, when people ``innovate'', they could set the cultural traits anywhere in it's \emph{space state}\footnote{The differents form that the given traits could talk}, whereas in Gintis the trait mutate in a fixed proportion depending on its previous value.

@@

As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law.
